---
title: "20190121_MiBand"
author: "Clara"
date: '2019-01-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning = FALSE)
```

## Sleep Periodiocity
```{r cars}
sleep=read.csv("Ben's 30-day sleep.csv")

library(scales)
library(xts)
library(data.table)
library(ggplot2)
library(zoo)
require(dplyr)
library(chron) 

sleep$SStart=strptime(sleep$SleepStart,"%Y-%m-%d %H:%M")
sleep$SEnd=strptime(sleep$SleepEnd,"%Y-%m-%d %H:%M")

sleep$midtime <- as.POSIXct((as.numeric(sleep$SStart) + as.numeric(sleep$SEnd)) / 2, origin = '1970-01-01')

# create chron object "times"
sleep$onlytime <- times(strftime(sleep$midtime,"%H:%M:%S"))
sleep_update=subset(sleep,sleep$SStart!=sleep$SEnd)
summary(sleep_update$onlytime) 
std=chron::times(sd(chron::times(sleep_update$onlytime)))
std
sleep_update$within1std=((mean(sleep_update$onlytime)-std < sleep_update$onlytime) & (mean(sleep_update$onlytime)+std > sleep_update$onlytime))
# 5 out of 15 days the patient mid-time slept later or earlier within one standard deviation
```

## Sleep Latency
```{r}
raw=read.csv('L1extract_raw.csv')
raw$time=strptime(raw$time,"%Y-%m-%d %H:%M")
plus1204=read.csv("Ben's PA data 1128to1205.csv")
plus1204$time=strptime(plus1204$time,"%Y-%m-%d %H:%M")
plus1204$description=ifelse(plus1204$description=='Walk'|plus1204$description=="Run",'active',as.character(plus1204$description))
data1204=subset(plus1204,as.Date(plus1204$time)=="2018-12-04")
raw_plus1204=rbind(subset(raw,as.Date(raw$time) %in% as.Date(sleep_update$Date)),data1204)

#actualSStartindex=vector("list", 15)
#for (i in 1:15) {
  #actualSStartindex[[i]]=match('Sleep',raw_plus1204$description[as.Date(raw_plus1204$time)==as.Date(sleep_update$Date[i])])
#}

sleep_update$latency[1]=difftime(raw_plus1204$time[min(which(raw_plus1204$description[as.Date(raw_plus1204$time)=='2017-04-08']=='Sleep'))],sleep_update$SStart[1],units = 'min')
sleep_update$latency[2]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-04-09'][226],sleep_update$SStart[2],units = 'min')
sleep_update$latency[3]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-04-10'][172],sleep_update$SStart[3],units = 'min')
sleep_update$latency[4]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-04'][76],sleep_update$SStart[4],units = 'min')
sleep_update$latency[5]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-10'][23],sleep_update$SStart[5],units = 'min')
sleep_update$latency[6]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-11'][18],sleep_update$SStart[6],units = 'min')
sleep_update$latency[7]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-12'][189],sleep_update$SStart[7],units = 'min')
sleep_update$latency[8]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-15'][45],sleep_update$SStart[8],units = 'min')
sleep_update$latency[9]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-16'][50],sleep_update$SStart[9],units = 'min')
sleep_update$latency[10]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-17'][141],sleep_update$SStart[10],units = 'min')
sleep_update$latency[11]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-18'][22],sleep_update$SStart[11],units = 'min')
sleep_update$latency[12]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-19'][1],sleep_update$SStart[12],units = 'min')
sleep_update$latency[13]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-20'][136],sleep_update$SStart[13],units = 'min')
sleep_update$latency[14]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2017-08-21'][163],sleep_update$SStart[14],units = 'min')
sleep_update$latency[15]=difftime(raw_plus1204$time[as.Date(raw_plus1204$time)=='2018-12-04'][178],sleep_update$SStart[15],units = 'min')

```
Question: is it likely to be, if today the patient goes to sleep earlier than yesterday/these days/usual, then today's sleep latency would be higher ?

## Generalized estimating equations (GEE) & Generalized linear mixed-effects model(GLMM)

Are strategies for longitudinal data analysis. 
Repeated measures: Include all data in a regression model for the mean response and account for longitudinal and/or cluster correlation

GEE: 
Contrast average outcome values across populations of individuals ⋆ defined by covariate values, while accounting for correlation
```{r}
#geeglm
#Specified by a mean model and a correlation model
#mean model assumptions：
#1.observations are independent across subjects
#2. observations could be correlated within subjects
```

GLMM:
Contrast outcomes both within and between individuals
• Assume that each subject has a regression model characterized by subject-specific parameters: a combination of fixed-effects parameters common to all individuals in the population and random-effects parameters unique to each individual subject
• Although covariates allow for differences across subjects, typically cannot measure all factors that give rise to subject-specific variation
```{r}
#GEE should be our case, but is our data longitudinal data or cross-sectional data? 
```

## Reclassification of 'idles with non-zero steps' using Amelia

Assume it's cross-sectional data
```{r}
require(Amelia)

setwd("/Users/xiaoyingzhang/Desktop/My Research with Ben")
raw$RawSensorData=ifelse(raw$description=="Idle"&raw$steps!=0&raw$RawSensorData>46,NA,raw$RawSensorData)
hist(raw$RawSensorData,breaks=100)
raw$time=strptime(raw$time,"%Y-%m-%d %H:%M")
#raw$time=unlist(raw$time)

library(lubridate)
raw_update=ts(raw)
a.out2 <- amelia(as.data.frame(raw_update), m=5,ts = "time",ords = 'description',lags = "RawSensorData",leads = "RawSensorData")
a.out2
save(a.out2, file = "imputations.RData")
# the ith imputed datasets can be retrieved from this list as a.out$imputations[[i]].
# In addition, save each of the imputed datasets to its own file:
write.amelia(obj=a.out2, file.stem = "outdata")

```

See excel file Reclassified for results.
Max difference: 60
Mean difference: -0.13
Std: 5.62
